A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-18 manuscript.Rmd
some modifications to rerun()

Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
For example, you can download any git repository with these commands:

@@

Projects that combine Make and Docker and adhere to the standard proposed by @Peikert2019 can be reproduced with:

@@

Because you probably want to reproduce your own project each time something changes, you will often want to reproduce everything.
The `repro`-package contains a function designed for that purpose:

@@

This function automatically figures out how to reproduce a project and also recognizes other employed reproducibility tools (like `renv` and `singularity`), but can of course only guess the appropriate way to reproduce a project.

If you have written a [Preregistration as Code] you can add the real data file to the project and reproduce the entire project with this single command.
In fact, until after we preregistered the study `r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below based on simulated data.
Only after we preregistered the whole manuscript and upon submission, they were based on actual data from https://openpsychometrics.org/_rawdata/.

>>>>

Ideally, you have a statement in the README that contains a short description of how to reproduce the project, whereas most steps are automatic and standardized.
This statement should also list all software requirements.
<!--AP: I think this Figure is superfluous. Please remove. All the information is in the following code blocks.-->
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
For example, you can download any git repository with these commands:

@@

Projects that combine Make and Docker and adhere to the standard proposed by @Peikert2019 can then be reproduced with:

@@

Typically there is a need to repeatedly reproduce a project during the development phase (e.g., on every change of  the analysis cod or, every change to the dataset).
The `repro`-package contains a function to reproduce all targets:

@@

This function automatically figures out how to reproduce an entire project and also recognizes non-default reproducibility tools (like `renv` and `singularity`). 
Of course, this automatic derivation of tools and steps is limited to the packages we have discussed here and the program may not always succeed if researchers deviate from our suggestions.

If you have written a [Preregistration as Code] you can add the real data file to the project and (re)produce the entire project with this single command.
In fact, until after we preregistered the study `r link("https://github.com/aaronpeikert/repro-tutorial/releases/tag/ v0.0.1-preregistration", "preregistration")` were the results below based on simulated data.
Only after we preregistered the whole manuscript and upon submission, they were based on actual data from https://openpsychometrics.org/_rawdata/.
